---
title: "TcPlus"
author: "Paul Sztorc"
date: "Wednesday, September 17, 2014"
output: html_document
---


The Goal: Reduce audit cost (it is currently a 'binding constraint').
Making auditing between only a few choices.

```{r Load,echo=FALSE,message=FALSE}
#Cleanup
rm(list=ls())

#Load everything
tryCatch(expr=setwd("~/GitHub/Truthcoin/lib"), error=function(e) setwd(choose.dir(caption="Failed to set working directory automatically. Choose 'Truthcoin/lib' folder:")) )
source(file="consensus/ConsensusMechanism.r")

Use <- function(package) { if(suppressWarnings(!require(package,character.only=TRUE))) install.packages(package,repos="http://cran.case.edu/") ; require(package,character.only=TRUE) }
```


Low Effort Auditing
===============================
```{r Data}

R <- c(.40, .25, .10, .10, .05, .05, .05)

VM <- matrix( c(1, 0, 0, 0, 0,
                1, 0, 0, 0, 0,
                1, 0, 0, 0, 0,
                1, 0, 0, 0, 0,
                1, 0, 0, 0, 0,
                1, 0, 0, 0, 0,
                1, 0, 0, 0, 0), 7,5,byrow=TRUE)

VM2 <- matrix(c(1, 0, 0, 0, 0,
                1, 0, 0, 0, 0,
                0, 0, 0, 0, 0,
                0, 0, 0, 0, 0,
                0, 0, 0, 0, 0,
                0, 0, 0, 0, 0,
                0, 0, 0, 0, 0), 7,5,byrow=TRUE)

VM3 <- matrix(c(1, 0, 0, 0, 0,
                1, 0, 0, 0, 0,
                0, 1, 0, 1, 0,
                0, 0, 0, 0, 1,
                0, 0, 0, 0, 0,
                0, 0, 0, 0, 1,
                0, 0, 0, 0, 1), 7,5,byrow=TRUE)

VM4 <- matrix(c(1, 0, 0, 0, 0,
                1, 0, 0, 0, 0,
                .5, 0, 0, 0, 0,
                .5, 0, 0, 0, 0,
                0, 0, 0, 0, 0,
                0, 0, 0, 0, 0), 6,5,byrow=TRUE)

VM5 <- matrix(c(0.0, 1.0, 0.81, 0.20, 0.03,
                0.0, 1.0, 0.79, 0.20, 0.04, # confused
                0.0, 1.0, 0.80, 0.20, 0.02,
                0.0, 1.0, 0.80, 0.20, 0.03,
                0.0, 1.0, 0.80, 0.98, 0.55, # liars spamming
                0.0, 1.0, 0.80, 0.97, 0.56, # liars spamming
                0.0, 1.0, 0.80, 0.99, 0.57), # liars spamming
              7, 5, byrow=TRUE)

# drawing it out of the binary ballot - cuts everything in half
VM6 <- matrix(c(0.8, 0.0, 0.0, 0.25, 0.045,
                0.6, 0.5, 0.5, 0.20, 0.030,
                0.4, 1.0, 1.0, 0.15, 0.015),
              3, 5, byrow=TRUE)

R6a <- c(.34,.32,.34)

R2 <- c(.40, .20, .20, .17, .01, .01, .01)

```

```{r Ballots}
Use('reshape2')

GetUniqueBallots <- function(VoteMatrix, Reputation = DemocracyRep(VoteMatrix)) {
  # Takes a VoteMatrix and Reputation, and returns a minimal set of unique Ballots.
  
  Rep_VM <- matrix(c(Reputation,VoteMatrix), nrow = nrow(VoteMatrix))
  
  # Force Unique Names
  colnames(Rep_VM) <- c( "Rep", paste("D",1:(ncol(Rep_VM)-1), sep=".") )
  
  # Get the unique ballots ("unique"), but ignore non-unique VTC ownership ( " [,-1]" ).
  Map1 <- data.frame( unique(Rep_VM[,-1]) ) 
  
  # Relabel (for upcoming merge)
  names(Map1) <- colnames(Rep_VM)[-1] # Again, we're dropping "Rep"
  
  # Give each Ballot a LETTER label
  Map2 <- cbind( Map1, "BallotGroup"= factor(LETTERS[1:nrow(Map1)]) )

  # Vote Matrix, with labelled Ballots
  Merg <- merge(Rep_VM,Map2)
  MergSub <- Merg[,c("Rep","BallotGroup")]
  
  # Aggregate Ballots
  Map3 <- dcast(MergSub, formula = BallotGroup~., fun.aggregate = sum, value.var = "Rep") #
  names(Map3) <- c("BallotGroup","BallotRep")
  
  Merg2 <- merge(Map3,Map2)
  if( !is.null(colnames(VoteMatrix)) ) names(Merg2) <- c( names(Merg2)[1:2], colnames(VoteMatrix) ) # restore original column names (if the given VM had colnames)
  return(Merg2)
}

GetUniqueBallots(VoteMatrix = VM3, R)
#   BallotGroup BallotRep D.1 D.2 D.3 D.4 D.5
# 1           A      0.65   1   0   0   0   0
# 2           B      0.10   0   1   0   1   0
# 3           C      0.20   0   0   0   0   1
# 4           D      0.05   0   0   0   0   0


GetUniqueBallots(VoteMatrix = VM4)
#   BallotGroup BallotRep D.1 D.2 D.3 D.4 D.5
# 1           A 0.3333333 1.0   0   0   0   0
# 2           B 0.3333333 0.5   0   0   0   0
# 3           C 0.3333333 0.0   0   0   0   0

GetUniqueBallots(VoteMatrix = VM5)
#   BallotGroup BallotRep D.1 D.2  D.3  D.4  D.5
# 1           A 0.1428571   0   1 0.81 0.20 0.03
# 2           B 0.1428571   0   1 0.79 0.20 0.04
# 3           C 0.1428571   0   1 0.80 0.20 0.02
# 4           D 0.1428571   0   1 0.80 0.20 0.03
# 5           E 0.1428571   0   1 0.80 0.98 0.55
# 6           F 0.1428571   0   1 0.80 0.97 0.56
# 7           G 0.1428571   0   1 0.80 0.99 0.57

GetUniqueBallots(VM6,Reputation = R6a)
#   BallotGroup BallotRep D.1 D.2 D.3  D.4   D.5
# 1           A      0.34 0.8 0.0 0.0 0.25 0.045
# 2           B      0.32 0.6 0.5 0.5 0.20 0.030
# 3           C      0.34 0.4 1.0 1.0 0.15 0.015
```


We have succeeded in paritioning the VoteMatrix into selections. Auditors need only choose their favorite Ballot.

Can we do better?
1. An attacker will likely distort many Decisions at once, to maximize the Attack Revenue.
2. Double-Factory will already sort out only the contested Decisions.
3. It takes effort for each Auditor to consider each Ballot. Fewer Ballots = Less Effort, Easier Audit.
4. Likely, some attacked-Decisions will be extremely-obviously false (a claim that Romney was elected in 2012).

Auditors should be doing MUCH less work than Voters.
Reducing to an 0 / 1 Ballot Referendum easily allows reuse of the existing SVD consensus system.

Goal: Reduce many unique Ballots to a maximally-representative set of 2 or 3.
Strategy: calculated 'Moved Reputation' and minimize it.

EasyAuditing
==========================

```{r BallotDistances}


GetTravelMatrix <- function(UniqueBallotDf) {
  # Takes the results computed by 'GetUniqueBallots' and uses them to build a matrix describing how different the Ballots are from each other.
  
  nBals <- nrow(UniqueBallotDf)
  
  DistMat <- matrix(0, nBals, nBals,dimnames = list(UniqueBallotDf$BallotGroup, UniqueBallotDf$BallotGroup))
  
  for(i in 1:nBals) { # for each Ballot-Group A, B, C...
    for(j in 1:nBals) { # for each other Ballot-Group A, B, C...
      if(i!=j) { # Diagonals will always be zero
        
        RowDifference <- UniqueBallotDf[i,-1:-2] - UniqueBallotDf[j,-1:-2] # How different are these rows?
        Distance <- sum( abs( RowDifference ) ) # Aggregate distance
        DistMat[i,j] <- Distance
        
        }
      }
    }
  
  DistMat
  
  TravelMat <- diag(UniqueBallotDf$BallotRep) %*% DistMat
  row.names(TravelMat) <- colnames(TravelMat)
  
  return(TravelMat)
}


GetTravelMatrix( GetUniqueBallots(VoteMatrix = VM3, R) )
#      A    B    C    D
# A 0.00 1.95 1.30 0.65
# B 0.30 0.00 0.30 0.20
# C 0.40 0.60 0.00 0.20
# D 0.05 0.10 0.05 0.00

GetTravelMatrix( GetUniqueBallots(VoteMatrix = VM4) )
#           A         B         C
# A 0.0000000 0.1666667 0.3333333
# B 0.1666667 0.0000000 0.1666667
# C 0.3333333 0.1666667 0.0000000
```

```{r BallotPooling}
# Now, our pooling algorithm


Use('combinat')


GetChosen <- function(TravMat, ExtractN = 2) {
  # Takes a matrix of travel-distances ("from" row-Ballot "to" column-Ballot) and finds the two nearest destinations (columns)
  
  Options <- combn(colnames(TravMat), ExtractN)
  
  BallotPairs <- vector("numeric", ncol(Options))
  
  # Get Chosen
  for(i in 1:ncol(Options)) {
    
    ThisDestination <- Options[,i]
    
    # remove rows where the rowname matched the entries in this Option-column
    # "In a world where these Ballots are staying put (not going from anywhere to anwhere)."
    
    TravMatTemp <- TravMat[ , colnames(TravMat) %in% ThisDestination ]   # everyone must come to these rows
    TravMatTemp <- TravMatTemp[ !( row.names(TravMatTemp) %in% ThisDestination ) ,] # these rows aren't going anywhere
    
    if(class(TravMatTemp) =="numeric") {
      # In this case, we've removed all rows except one.
      BallotPairs[i] <- sum(TravMatTemp) # Total distance
      }
    
    if(class(TravMatTemp) =="matrix") {
      # Normal case
      ColMins <- apply( TravMatTemp, 1, function(x) x[which.min(x)]) # shortest path to a destination
      BallotPairs[i] <- sum(ColMins) # Total distance
      }
    
    # If TravMatTemp is of a different class, it is probably empty (and we can leave the distances at zero).
    }
  
  Chosen <- Options[ , which.min(BallotPairs) ]
  return(Chosen)
}

GetChosen( GetTravelMatrix( GetUniqueBallots(VoteMatrix = VM3, R) ) )

GetChosen( GetTravelMatrix( GetUniqueBallots(VoteMatrix = VM4) ) ) 



GetAuditChoices <- function(VoteMatrix, Reputation = DemocracyRep(VoteMatrix)) {
  # Putting it all together.
  
  # Call our functions.
  Ballots <- GetUniqueBallots(VoteMatrix, Reputation)
  Distance <- GetTravelMatrix(Ballots)
  
  # Filter small fish / spam Ballots ( because I will be doing combinatorial math next)
  SeriousCandidates <- Distance[, Ballots$BallotRep >= .05 ] # might change ".05" to the Branch's (1-Phi)
  
  # Grab the most-representative choices, and don't stop grabbing until you have enough
  CumulativeReputation <- 0
  ExtractN <- 2
  while(CumulativeReputation < .80) {  # ".80" should definitly be (1-Phi)
    Chosen <- GetChosen(SeriousCandidates, ExtractN)
    CumulativeReputation <- sum( Ballots[ Ballots$BallotGroup %in% Chosen , "BallotRep" ] )
    ExtractN <- ExtractN + 1
  }
  
  # For simplicity
  InChosen <- ( row.names(Distance) %in% Chosen )
  
  # Create two dataframes
  Choices <- Ballots[ InChosen , ]
  NonChoices <- Ballots[ !(InChosen) , ]
  
  # Get some info to tell people which Ballots contain which.
  NonChDist <- as.matrix( Distance[ !(InChosen) , InChosen ] )
  
  NonChoices$SurrogateChoice <- apply( NonChDist, 1, function(x) colnames(NonChDist)[which.min(x)] )
  
  return(list("Choices"=Choices,"NonChoices"=NonChoices))
  
}

GetAuditChoices(VM4)

GetAuditChoices(VM3, R) 
GetAuditChoices(VM3, R2) 

GetAuditChoices(VM5)
GetAuditChoices(VM5, R2)

GetAuditChoices(VM6, R6a) 
# Here, we've succeeded in drawing the 'real' ballot (B) off, using 68% of the votes. However, B still has a surrogate choice ("C")
# B will deterministically have a unique surrogate choice (not a "Tie") unless every single Decision was scaled and had a real outcome of exactly ".5" (which is nearly impossible).


```



Double Factory Examination
===========================================
```{r DefineDoubleFact}

Use('ggplot2')
try( detach("package:reshape", unload=TRUE) ) # version control...
Use('reshape2')

## What effect does DoubleFactory have?

Dim <- 20

ContAmb <- matrix(0,(Dim-1),(Dim-1))
ContAmb[ lower.tri(ContAmb, diag = TRUE) ]  <- 1

# Balance the matrix
ContAmb <- cbind(ContAmb,0) 

# Add a few 'right answers'
ContAmb <- rbind(ContAmb[1:9,],
                 ContAmb[9,], ContAmb[9,],
                 ContAmb[10,], ContAmb[10,],
                 ContAmb[10:19,] ) 

colnames( ContAmb ) <- paste("D.",1:(ncol(ContAmb)), sep="") 
row.names( ContAmb ) <- paste("Voter.",1:(nrow(ContAmb)), sep="") 

ContAmb


DoubleFactoryTest <- function(X, Scales = BinaryScales(X), Rep = DemocracyRep(X), CatchP=.1, MaxRow=5000, Phi=.65, Verbose=FALSE, PrintSurvivors = TRUE) {
  # Runs Factory Twice and checks on what happened as a result
  
  WaveOne <- Factory(X,Scales,Rep,CatchP,MaxRow,Verbose)
  
  if(Verbose) print(" Wave One Complete.")
  
  
  # Find the contested contracts
  Safe  <- ( WaveOne$Decisions["Certainty",] >= Phi )# all those contracts which were unanimous for a subset of proportion ("Phi")
  
  # What if they ALL were contested?
  if( sum(Safe)==0 ) {
    print("Consensus Failure!! ..printing Wave one")
    print("Consensus Failure!! ..printing Wave one")
    print("Consensus Failure!! ..printing Wave one")
    return(WaveOne)
    }
  
  if(PrintSurvivors) {
    print( sum(Safe)/ncol(X) ) # proportion which made it
    print( X[,Safe] )          # the new matrix
  }
  
  WaveTwo <- Factory( X[,Safe] ,
                      Scales[,Safe],
                      Rep,CatchP,MaxRow,Verbose)
  
  Results <- matrix( c( ( WaveOne$Agents[,"RowBonus"] - WaveOne$Agents[,"OldRep"] ),
                        ( WaveTwo$Agents[,"RowBonus"] - WaveTwo$Agents[,"OldRep"] ) ),
                     ncol=2,
                     dimnames=list(rownames(X),c("Gain.W1","Gain.W2")) )
  
  mRes <- melt(Results)
  cRes <- dcast(mRes,formula=Var1~Var2,fun.aggregate=sum)
  
  Results <- cbind(Results, "Diff"=Results[,2]-Results[,1])
  
  PlotResults <- data.frame( cbind(Results, "Voter"=factor( 1:(nrow(Results)) )) )
  mPR <- melt(PlotResults,id.vars="Voter")
  
  P1 <- ggplot(mPR, aes(y=value, x=Voter, fill=factor( Voter ) )) +
    geom_bar(stat="identity", position = "dodge") +
    theme(legend.position="none") +
    facet_grid(variable~.)
  
  print(P1)
  
  return(Results)
  
}

```

```{r Tests}

DoubleFactoryTest(ContAmb)
# Comment: Here, because of this amusingly-unrealistic Voting Matrix (where nearly everyone is equally confused about everything),
# ...the 'Reference Index' is at zero. The software cannot establish a reference case, and is essentially indifferent.
# This is why Voters 1-8 benefit and 15-23. This is arbitrary and unstable, and might flip with just a fractional increase in 15-23 coordination.
# Double Factory seems to help in this case: the middle groups become more coordinated and less arbitrary.

ContAmb2 <- ContAmb
ContAmb2["Voter.23", "D.18"] <- 0 # The most profitable deviation (?)

DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)
# Voter 23 has sent his report skyrocketing...
DoubleFactoryTest(ContAmb, PrintSurvivors = FALSE)["Voter.23","Gain.W2"] # -0.004347826
DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)["Voter.23","Gain.W2"] # 0.003491191
# ...but the core group is mostly unaffected (improving slightly).
DoubleFactoryTest(ContAmb, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0003981117
DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0004388715


# The obvious counter-move:
ContAmb3 <- ContAmb2
ContAmb3["Voter.1", "D.3"] <- 1 # The most profitable deviation (?)

DoubleFactoryTest(ContAmb3)
# Voter 1 has reclaimed his position...
DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)["Voter.1","Gain.W2"] # -0.004347826  -- notice that this is actually the same as ContAmb1 Voter 23!
DoubleFactoryTest(ContAmb3, PrintSurvivors = FALSE)["Voter.1","Gain.W2"] # 0.003792857
# ...and the core group still marches slowly toward victory.
DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0004388715
DoubleFactoryTest(ContAmb3, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0004328065

# Repeat repeat repeat...
ContAmb4 <- ContAmb3
ContAmb4["Voter.22", "D.17"] <- 0
ContAmb4["Voter.21", "D.16"] <- 0
ContAmb4["Voter.20", "D.15"] <- 0
# Voter 22 ...
DoubleFactoryTest(ContAmb3, PrintSurvivors = FALSE)["Voter.22","Gain.W2"] # -0.004347826
DoubleFactoryTest(ContAmb4, PrintSurvivors = FALSE)["Voter.22","Gain.W2"] # 0.003074838
# ...march, march, march.
DoubleFactoryTest(ContAmb3, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0004328065
DoubleFactoryTest(ContAmb4, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0006672369


```


```{r PhiEffect}

DoubleFactoryTest(ContAmb, Phi = .55)

DoubleFactoryTest(ContAmb, Phi = .70)

DoubleFactoryTest(ContAmb, Phi = .90)

DoubleFactoryTest(ContAmb, Phi = .95)

# The effect is clear: more stablity. W2 is simply "flatter" and less subject to the arbitrary tiebreaker of the Reference Index.

```


```{r BumpingInAndOut}

Bump <- ContAmb

Unbumped <- DoubleFactoryTest(Bump)

#Voter 8 Bumps Decision 8
Bump2 <- Bump
Bump2["Voter.8","D.8"] <- 0
Bumped <- DoubleFactoryTest(Bump2)

Unbumped["Voter.8","Gain.W2"]
Bumped["Voter.8","Gain.W2"]
# This is kind of strange...

# (1) There is a more profitable move availiable to Voter.8
# (2) This is a function of this strange matrix specifically

Bump3 <- Bump
Bump3["Voter.8","D.9"] <- 1

Unbumped["Voter.8","Gain.W2"]
DoubleFactoryTest(Bump3)["Voter.8","Gain.W2"]
# Ha, this is interesting...Voter 8 accidentally de-coordinated his misinformed group.

Bump <- matrix(0,(Dim-1),(Dim-1))
colnames( Bump ) <- paste("D.",1:(ncol(Bump)), sep="") 
row.names( Bump ) <- paste("Voter.",1:(nrow(Bump)), sep="") 
Bump[1:9,"D.1"] <- 1

DoubleFactoryTest(Bump)

# Clearly, if someone "un-Bumps" Decision 1, the "Bumpers" are screwed.

```


```{r Synthesis}

# Outcome of Phi / DoubleFactory
M_res <- M1[,2:3]

GetUniqueBallots( M_res )

GetAuditChoices( M_res )

GetContestedDecisions <- function(M) {
  # Puts a few pieces together
  
  Uncontested <- colnames( DoubleFactory(M)$Filled )
  ContestedMatrix <- M[,! (colnames(M) %in% Uncontested) ] # notice "!"
  return( GetAuditChoices( ContestedMatrix ) )
}

GetContestedDecisions(M1)
# $Choices
#   BallotGroup BallotRep D2.1 D3.0
# 1           A 0.3333333    1    0
# 4           D 0.3333333    0    1
# 
# $NonChoices
#   BallotGroup BallotRep D2.1 D3.0 SurrogateChoice
# 2           B 0.1666667    0    0             Tie
# 3           C 0.1666667    1    1             Tie

# Notice something interesting:
GetAuditChoices( M )
GetAuditChoices( M1[,2:3] )

# Notice also that I am NOT using SVD on purpose:
# [1] If we make it to this point, the attacker will have >50% ...
# [2] SVD had a specific purpose of measuring disagreement with the majority. However, this case is a failure-to-find-majority.

BigM1 <- cbind( M1, M1, M1, M1[,-3])

DoubleFactoryTest(BigM1)
GetContestedDecisions(BigM1)
PlotJ(BigM1)



#
colnames(VM6) <- paste("D",1:5,sep = ".")
Scales6 <- BinaryScales(VM6)
Scales6["Scaled",] <- TRUE
DoubleFactoryTest(VM6, Scales = Scales6, Rep = R6a)
GetAuditChoices(VM6,Reputation = R6a)
# This seems to be a successful attack ... but how strategically stable is it?

# ...if the 68% group waivers a little:
R6b <- c(.34, .32001, .33999)
GetAuditChoices(VM6,Reputation = R6b)
# $Choices
#   BallotGroup BallotRep D.1 D.2 D.3  D.4   D.5
# 1           A   0.34000 0.8   0   0 0.25 0.045
# 3           C   0.33999 0.4   1   1 0.15 0.015
# 
# $NonChoices
#   BallotGroup BallotRep D.1 D.2 D.3 D.4  D.5 SurrogateChoice
# 2           B   0.32001 0.6 0.5 0.5 0.2 0.03               C

# this results favors increasing the unique Ballots to 3, (perhaps, IF the current Ballots do not contain enough residual vote-distance)

# let's go back and add that.


# (later) ...added.

```



