Tests, Results, and Commentary
========================================================
Dec 3, 2013

```{r Load,echo=FALSE,message=FALSE}
#Cleanup
rm(list=ls())

#Load everything
tryCatch(expr=setwd("~/GitHub/Truthcoin/lib"), error=function(e) setwd(choose.dir(caption="Failed to set working directory automatically. Choose 'Truthcoin/lib' folder:")) )
source(file="consensus/ConsensusMechanism.r")
```


```{r Tools,echo=FALSE,message=FALSE}

#1 - Who benefited this round?
CompareIncentives <- function(X,FF=Factory,N=1) {
  Dim <- dim(X)
  Results <- data.frame('Group'=row.names(X))
  Results <- suppressWarnings( cbind(Results, Chain(X,N=N)[[N]]$Agents[,c("OldRep","SmoothRep")] ) )
  Results$Drep <- Results$SmoothRep - Results$OldRep
  
  Groups <- aggregate( . ~ Group, Results, sum)
  Groups <- Groups[order(Groups$Drep,decreasing=TRUE),]
  
  Out <- vector("list",2)
  Out[[1]] <- Results
  Out[[2]] <- Groups
  return(Out)
}


Chain <- function(X, Scales = BinaryScales(X), N = 2, ThisRep = DemocracyRep(X)) {
  # Repeats factory process N times

  Output <- vector("list")
  for(i in 1:N) {
    Output[[i]] <- Factory(X,Scales,Rep=ThisRep)
    ThisRep <- Output[[i]]$Agents[,"RowBonus"]
  }
  
  return(Output)
}


source(file="consensus/PlotJ.r")
```


```{r DeclareScenarios,echo=FALSE,message=FALSE}

#Declare Big List of "Scenarios to Check"
Scenarios <- vector("list")
SLabels <- vector("list")

#[1] Design Case
SLabels$Base <- "Basic Case - 14/24 [58%] Honest"

M1 <-  rbind(
    c(1,1,0,0),
    c(1,0,0,0),
    c(1,1,0,0),
    c(1,1,1,0),
    c(0,0,1,1),
    c(0,0,1,1))
  
row.names(M1) <- c("Honest", "Confused 1", "Honest", "Confused 2", "Liar", "Liar")
colnames(M1) <- c("D1.1","D2.1","D3.0","D4.0")

Scenarios$Base <- M1

M1disp <- M1
row.names(M1disp) <- paste("Voter",1:nrow(M1))
#


# [2] Reversed Matrix
SLabels$Reversed <- "Basic Case - 14/24 [58%] Honest, reversed wording"
M2 <- ReverseMatrix(M1)
Scenarios$Reversed <- M2
#


# [3] Deviance: Deranged Nonconformist
SLabels$Deviance <- "Punishment from Deviating from Stable"

M3 <- rbind(M1[c(1,3),],
            M1[c(1,3),],
            "Liar"=c(0,0,1,1))

Scenarios$Deviance <- M3
#


# [4] Coalitional Deviance: Using a group to game the system.
SLabels$CoalitionalDeviance <- "Targeting Contract (#3) with <50% Conspirators (including 1 AntiTruth Diver)"
SLabels$CoalitionalDeviance2 <- "Targeting Contract (#3) with <50% Conspirators (including 1 AntiTeam Diver)"

 M4b <- rbind("True"=c(1,1,0,0),
              "True"=c(1,1,0,0),
              "True"=c(1,1,0,0),
              "True"=c(1,1,0,0),
              "True"=c(1,1,0,0),
              "True"=c(1,1,0,0),
              "Diver"=c(0,0,1,1), #Diver
              "Liar"=c(1,1,1,0),
              "Liar"=c(1,1,1,0),
              "Liar"=c(1,1,1,0), #4 conspirators           
              "Liar"=c(1,1,1,0)) # + 1 Diver     = 5 <6    

M4c <- M4b
M4c["Diver",3] <- 0 #Diver negatively correlated with his team

M4d <- rbind(M4c,"FailSafe"=c(.5,.5,.5,.5))


Scenarios$CoalitionalDeviance  <- M4b
Scenarios$CoalitionalDeviance2  <- M4c
#


# [5] Clueless: Passing on a Contract - "I have no idea"
SLabels$CluelessControl <- c("Having no idea - 'passing' on a contract [control]")  
SLabels$CluelessTest <- c("Having no idea - 'passing' on a contract [test]")  

M3a <- rbind(M1[1,],M1[1,],M1[1,],M1[1,],M1[1,],M1[1,],M1[1,]) #bigger reference case
row.names(M3a) <- rep("True",nrow(M3a))

M3m <- M3a
M3m[2,2] <- NA 

Scenarios$CluelessControl <- M3a 
Scenarios$CluelessTest <- M3m 
#

 
# [6] Inchoerence
SLabels$Incoherence <- c("Punishing Incoherence - I KNOW that this contract is spam/nonsense") 
SLabels$Incoherence2 <- c("Punishing Incoherence - I KNOW that this contract is spam/nonsense [2]") 

M6 <- M3a
M6[-3,2]  <- .5 #Incoherent

colnames(M6) <- c("D1.1", "D2.(.5)", "D3.0", "D4.0")
row.names(M6)[3] <- "Overconfident"
M6disp <- M6
row.names(M6disp) <- paste("Voter",1:nrow(M6))


M6b <- M6
M6b[7,2]  <- 0 #Incentive examination


Scenarios$Incoherence <- M6
Scenarios$Incoherence2 <- M6b
#
  




# [7] Unanimous: Perfect Consensus Bug
SLabels$Unanimous <- c("Having everyone agree perfectly (desireable) crashes PCA") 

PerCon <- rbind(M1[1,], M1[1,], M1[1,], M1[1,])

Scenarios$PerCon <- PerCon
#


# [8] Contract Gaming
SLabels$Gaming <- c("Gaming the Contracts") 

M9 <- cbind(M1,"C0.5"=.5,"C0.5"=.5,"C0.5"=.5,"C0.5"=.5,"C0.5"=.5,"C0.5"=.5,"C0.5"=.5,"C0.5"=.5)
M9[5:6,5:12] <- c(0,1,1,0)
M9 <- rbind(M9,M9,M9,M9)

Scenarios$Gaming <- M9
#


# [9] Handling Missing Values
SLabels$Missing1 <- c("A minority of players give missing values to 1 contract")
SLabels$Missing2 <- c("A majority of players give missing values to a minority of their contracts")
SLabels$Missing3 <- c("All players give missing values to a minority of their contracts")
SLabels$Missing4 <- c("Some players give missing values to a majority of their contracts")
SLabels$Missing5 <- c("All players give missing values to a majority of their contracts")

M10a <- cbind(M1,"D5.0"=c(0,NA,0,NA,1,1))

M10b <- cbind(M10a, "D6.1"=c(1,1,1,NA,0,0), "D6.0"=c(NA,NA,NA,0,1,1))
M10b <- rbind(M10b,M10b)

M10c <- M10b
M10c[5,1] <- NA ; M10c[6,2] <- NA ; M10c[11,1] <- NA ; M10c[12,2] <- NA ;

M10d <- M10b[-11:-12,]
M10d[5,3:6] <- NA ; M10d[6,1:4] <- NA ; 
M10d[7:8,1:2] <- NA ; M10d[2,2:3] <- NA;

M10e <- rbind(M1,M1)
M10e <- cbind(M10e[,1],M10e,M10e)

M10e[1,1:5] <- NA
M10e[2,2:6] <- NA
M10e[3,3:7] <- NA
M10e[4,4:8] <- NA
M10e[5,5:9] <- NA
M10e[6,c(6:9,1)] <- NA
M10e[7,c(7:9,1:2)] <- NA
M10e[8,c(8:9,1:3)] <- NA
M10e[9,c(9,1:4)] <- NA
M10e[10,1:5] <- NA
M10e[11,2:6] <- NA
M10e[12,3:7] <- NA

Scenarios$Missing1 <- M10a
Scenarios$Missing2 <- M10b
Scenarios$Missing3 <- M10c
Scenarios$Missing4 <- M10d
Scenarios$Missing5 <- M10e
#


# [10] Riven Judgements
SLabels$Riven <- "Separate but equal subgroups, and their recombination. [1]" 
SLabels$Riven2 <- "Separate but equal subgroups, and their recombination. [2]" 

Mg <- rbind( cbind(M1,   M1*NA, M1*NA),
             cbind(M1*NA,M1,    M1*NA),
             cbind(M1*NA,M1*NA, M1))

Mg2 <- Mg
Mg2[7,1] <- 1


Scenarios$Riven <- Mg
Scenarios$Riven2 <- Mg2
#
```


Base
---------------

```{r Base}
Factory(Scenarios$Base)
CompareIncentives(Scenarios$Base)
#Good.
Chain(X=Scenarios$Base)
PlotJ(M=Scenarios$Base)
```

Very good. Conforms quickly to a correct prediction.
I'm thinking one block per day, or something, assuming we smooth difficulty correctly.

Reversed
---------------

```{r Reversed}
Factory(Scenarios$Reversed)
all.equal(Factory(Scenarios$Reversed)$Agents,Factory(Scenarios$Base)$Agents) #TRUE
```
Identical incentive structure, despite reversed inputs and outputs.
Good.

One Liar
------------------
```{r OneLiar}
Factory(Scenarios$Deviance)
```
Biggest Deviator gets CRUSHED to zero. High-Stakes!
Good.

Many Liars
-------------------

```{r ManyLiars}

Factory(Scenarios$CoalitionalDeviance)
#Success: An attempted <51% attack which failed.

Factory(Scenarios$CoalitionalDeviance2)
# Oh, no: A Sucessful <51% attack 'Friendly Fire' ...will have to address this.

  #Pre-Analytics
  CompareIncentives(X=Scenarios$CoalitionalDeviance2)
  
  row.names( Scenarios$CoalitionalDeviance2 )[7] <- "Liar"
  CompareIncentives(X=Scenarios$CoalitionalDeviance2)

  # [1] Success: 'Symmetric Friendly Fire'  (ie Team truth forms a coalition of their own)
  Scenarios$CoalitionalDeviance3 <- Scenarios$CoalitionalDeviance2
  Scenarios$CoalitionalDeviance3[6,] <- c(0,0,1,1)

  CompareIncentives(X=Scenarios$CoalitionalDeviance3)
```
  #Chain(Scenarios$CoalitionalDeviance3,N=100)
  #Team 'True' wins via symmetry-exploitation
```{r ManyLiars2}
  # [2] Success: 'Cold Feet 1' (a single player abandons the coalition)
  Scenarios$CoalitionalDeviance4 <- Scenarios$CoalitionalDeviance2
  Scenarios$CoalitionalDeviance4[8,] <- c(1,1,0,0)
  
  CompareIncentives(X=Scenarios$CoalitionalDeviance4)
  Ss <- Chain(Scenarios$CoalitionalDeviance4,N=70)[[70]]$Agents
  Ss <- data.frame(NewRep=as.numeric(Ss[,"RowBonus"]),Group=row.names(Ss))
  aggregate(.~Group,data=Ss, FUN=sum)

  Scenarios$CoalitionalDeviance5 <- Scenarios$CoalitionalDeviance2
  Scenarios$CoalitionalDeviance5[8,] <- c(1,1,0,0)
  Scenarios$CoalitionalDeviance5[9,] <- c(1,1,0,0)

  CompareIncentives(X=Scenarios$CoalitionalDeviance5)
  Ss <- Chain(Scenarios$CoalitionalDeviance5,N=50)[[50]]$Agents
  Ss <- data.frame(NewRep=as.numeric(Ss[,"RowBonus"]),Group=row.names(Ss))
  aggregate(.~Group,data=Ss, FUN=sum)
  #Notice after 50 rounds, the devil [=King of Liars] has actually become the two bottommost liars, as they represent the most significant source of confusion.
  #Team 'True' wins via stoicism

  #[3] Recursive Friendly Fire - a sub-coalition forms to defect, but a sub-coalition of this coalition forms to defect again.
  Scenarios$CoalitionalDeviance6 <- rbind(c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1), #10
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1),
                                          c(1,1,0,0,1), #15 (60%)
                                          
                                          #Coalition 1, backstabbing Truth to game contract 3
                                          c(0,0,0,1,0), #1 - Friendly Fire
                                          c(1,1,1,0,1),
                                          c(1,1,1,0,1),
                                          c(1,1,1,0,1),
                                          c(1,1,1,0,1),
                                          c(1,1,1,0,1), #6 (24%)
                                          
                                          #Coalition 2, 'backstabbing' Coalition 1 to game contract 4
                                          c(0,0,1,0,0), #1 - Friendly Fire
                                          c(1,1,0,1,1),
                                          c(1,1,0,1,1),
                                          c(1,1,0,1,1)) #4 (16%)

  row.names(Scenarios$CoalitionalDeviance6) <- c(rep('Truth',15),rep('Lie 1',6),rep('Lie 2',4))
  colnames(Scenarios$CoalitionalDeviance6) <- c("C1.1","C2.1","C3.0","C4.0","C5.1")
  Factory(Scenarios$CoalitionalDeviance6)
  CompareIncentives(Scenarios$CoalitionalDeviance6)
  #fantastic sucess...Lie 2 loses less

  #clearly, the Nash Equilibrium
  Scenarios$CoalitionalDeviance7 <- Scenarios$CoalitionalDeviance6[1:21,]
  Scenarios$CoalitionalDeviance7 <- rbind(Scenarios$CoalitionalDeviance7, rbind(
                                                                              'Truth 2'=c(1,1,0,0,1),
                                                                              'Truth 2'=c(1,1,0,0,1),
                                                                              'Truth 2'=c(1,1,0,0,1),
                                                                              'Truth 2'=c(1,1,0,0,1)))
  Factory(Scenarios$CoalitionalDeviance7)
  CompareIncentives(Scenarios$CoalitionalDeviance7)

  # [4] Passive - Sideways expansion by 2 contracts
  Scenarios$CoalitionalDeviance8 <- cbind(Scenarios$CoalitionalDeviance2,Scenarios$CoalitionalDeviance2[,1:2])
  Factory(Scenarios$CoalitionalDeviance8)
  CompareIncentives(Scenarios$CoalitionalDeviance8)   
  #Success, larger number of contracts makes this attack improbable.

  Scenarios$CoalitionalDeviance9 <- cbind(Scenarios$CoalitionalDeviance2,
                                          Scenarios$CoalitionalDeviance2,
                                          Scenarios$CoalitionalDeviance2,
                                          Scenarios$CoalitionalDeviance2[,-3])
  Factory(Scenarios$CoalitionalDeviance9)
  CompareIncentives(Scenarios$CoalitionalDeviance9)
  #The attack must expand proportionally.
```


Uninformed People
------------------

```{r Uninformed}
Factory(Scenarios$CluelessControl)
Factory(Scenarios$CluelessTest)
```
Finding: 2 falls from tie at 5th .11 to a tie at 7th with .07; no impact on other results: success.

[done] Note: Must be a discrete set of options: c(1,0,NA,.5)    ---- !!! by extention, Catch must be implemented in FillNA. Indeed, in this example our lazy character is punished twice.
otherwise there will likely be pragmatic individuals who rationally deviate to answers like ~.85 or ~.92 or some nonsense. [obviously]

Overwhelming Incoherence
--------------------------
```{r Incoherence}

Factory(Scenarios$Incoherence)
Factory(Scenarios$Incoherence2)
```
Interesting behavior, but incentive compatible, particularly given low Schelling Salience
Incentive to switch to the consensus .5

Perfect Consensus
--------------------
```{r PefectConsensus}
Factory(Scenarios$PerCon)
#No problems.
```

Gaming
----------------
```{r Gaming}

Factory(Scenarios$Gaming)
CompareIncentives(Scenarios$Gaming)
#more or less what i expected
```


Missing Values
-----------------

```{r MissingValues}

Factory(Scenarios$Missing1)
Factory(Scenarios$Missing2)
Factory(Scenarios$Missing3)

PlotJ(M=Scenarios$Missing3)

Factory(Scenarios$Missing4)
Factory(Scenarios$Missing5)
#Works


Factory(Scenarios$Riven)
Factory(Scenarios$Riven2)

```

Scaled Claims
----------------------------
```{r ScaledClaims}


#HoR party seats example

#add a new row
MS <- cbind(M1,  rbind(233,
                       199,
                       233,
                       250,
                       435,
                       435))
colnames(MS) <- c( colnames(MS)[-5], "C5.233")

#build non-default scales
Scales <- matrix( c( rep(FALSE,ncol(MS)),
                     rep(0,ncol(MS)),
                     rep(1,ncol(MS))), 3, byrow=TRUE, dimnames=list(c("Scaled","Min","Max"),colnames(MS)) )
Scales["Scaled",5] <- 1
Scales["Max",5] <- 435



#DJIA example

MS2 <- cbind(MS,  rbind(16027.59,
                       NA,
                       16027.59,
                       NA,
                       8001,
                       19999))

Scales2 <- cbind(Scales,rbind(1,8000,20000))

colnames(MS2) <- c( colnames(MS2)[-6], "C6.1602759")
colnames(Scales2) <- colnames(MS2)


#Edit catch to choose most-likely values (modal)

Factory(MS2,Scales2)
```


```{r Other}

# !!! Must FillNa with .5 FIRST, then average in, to prevent monopoly voting on brand-new contracts. (Actually, if it will eventually be ruled .5).

#Voting Across Time
#Later Votes should count more
#! ...simple change = ConoutFinal becomes exponentially smoothed result of previous chains.
#! require X number of chains (blocks) before the outcome is officially determined (two weeks?)

# Will need:
# 1] Percent Voted
# 2] Time Dimension of blocks.

#
# Possible solutions:
#   1 - sequential filling of NAs (sequential removal of columns) - pre-processing replace with average?
#   2 - what about the 'expert factor' idea? what happened to that?
#   3 - Completely replace FillNa with Reputations (lots of positives here)

#TO-DO
#Cascading reputation .6,.5,.3.,2., etc =   dexp(nrow(Mg))

#Mysterious behavior - loading only on first factor
#solutions
# 1- ignore. incentives will encourage filling out of contracts on 'obvious' events
# 2 - use later factors. Unknown what behavior could result from this
```


Additive Reputation
-------------------------------------
Is reputation completely additive? - Yes, now.

```{r AdditiveR}
Mar1 <- M1
r1 <- rep(1/6,6)

Mar2 <- M1[-6,]
r2 <- c(1/6, 1/6, 1/6, 1/6, 2/6)

Mar3 <- M1[c(1,2,4,5),]
r3 <- c( 2/6, 1/6, 1/6, 2/6)

Mar4 <- M1[c(1,2,4,5,6),]
r4 <- c( 2/6, 1/6, 1/6, 1/6, 1/6)

Factory(Mar1,Rep=r1)$Agents
Factory(Mar2,Rep=r2)$Agents
Factory(Mar3,Rep=r3)$Agents
Factory(Mar4,Rep=r4)$Agents

#Is reputation additive? Yes (excluding NA-born effects, we could correct with Rep/mean(Rep) but NA is not part of equilibrium so it shouldnt matter).
```


```{r Unknown}
Factory(Mg)$Agents[,c("OldRep","ThisRep","SmoothRep")]
Factory(Mg2)$Agents[,c("OldRep","ThisRep","SmoothRep")]
# True 1 of group 2 skyrockets ahead, as desired.

# upon reflection, I dont think this 'problem' is particularly bad.
```

```{r }
Mub1 <- matrix(c(1, 0, 1.0, 1,  0.4498141, 0, 0, 1, 1, 0.7488008,
                 0, 0, 0.5, NA, 0.4460967, 0, 0, 1, 0, 0.7488008,
                 1, 0, 1.0, 1,  0.4498141, 0, 0, 1, 1, NA), 3, byrow = TRUE)

Factory(Mub1, Verbose = TRUE)



```


Scalability
------------------
What are the computational limits?
Largely irrelevant because of branching, this is important for setting parameters correctly (and in general).

```{r Scalability,cache=FALSE}

TestLimit <- function(n1,n2,AddNa=1) {
  M_huge <- matrix(round(runif(n1*n2)),n1,n2)
  if(AddNa==1) M_huge[sample(1:(n1*n2),size=(n1*n2)/3)] <- NA
  Factory(M_huge)
}


system.time(print("1"))
system.time(TestLimit(100,10))
system.time(TestLimit(1000,100))
# user  system elapsed 
# 0.66    0.00    0.65

#system.time(TestLimit(10000,100))
#    user  system elapsed 
#    10.23    0.05   10.29



#system.time(TestLimit(100000,100))
#    user  system elapsed 
#  134.08    0.80  134.96 

#Solutions

# [1] - cap the number of rows
  # in its current state, it is basically unlimited - unrealistic
  # the first 100,000 votes are probably decentralized enough ...how low should this number go? (can be a f[ncol(Vmatrix)])
  # given that reputation is fully additive, this would discourage the spreading of reputations
  # this would also solve the "dust bust" question (ie suck up any accounts with tiny dust amounts of reputation)
  # can add the slow retarget to make this grow over the next thousand years (every 4 years?)

#after simply listing the specifics of this solution I realize it is the best candidate

#Actually all of this is irrelevant because code runs 100x faster on python
```

```{r RewardFunction}

RawVsReturn <- 0

TwoTeams <- matrix( rbind( c(0,0,1,1,0,0,1,1),
                           c(1,1,0,0,1,1,0,0)),nrow=2)

OtherEffect <- function(Own) {
  Other <- 1 - Own
  Results <- Factory(TwoTeams, Rep = c(Own,Other))
  End <-  Results$Agents[1,"RowBonus"]
  Gain <- (End - Own)
  if(RawVsReturn == 0) Gain <- Gain/Own
  return(Gain)
}

RF <- data.frame("PctAgree"=seq(.05, .95, by = .05))

RF$p100 <- vapply(RF$PctAgree,FUN =  OtherEffect, FUN.VALUE = 2)

YLab <- "Your Reward (Raw)"
if(RawVsReturn == 0) YLab <- "Your Reward (%)"
plot(p100~PctAgree, data=RF, xlab = "Agreement with Your Choices (%)", ylab= YLab)
abline(h=0, lty=2)

lines(p100~PctAgree, data=RF)



TwoTeams <- matrix( rbind( c(NA,0,1,1,0,0,1,1),
                           c(1,1,0,0,1,1,0,0)),nrow=2)

RF$p088 <- vapply(RF$PctAgree, FUN =  OtherEffect, FUN.VALUE = 2)
lines(p088~PctAgree, data=RF, col=2, lty=3)

TwoTeams <- matrix( rbind( c(NA,0,1,1,NA,0,NA,1),
                           c(1,1,0,0,1,1,0,0)),nrow=2)

RF$p063 <- vapply(RF$PctAgree, FUN =  OtherEffect, FUN.VALUE = 2)
lines(p063~PctAgree, data=RF, col=3, lty=4)

TwoTeams <- matrix( rbind( c(NA,0,NA,1,NA,0,NA,NA),
                           c(1,1,0,0,1,1,0,0)),nrow=2)

RF$p038 <- vapply(RF$PctAgree, FUN =  OtherEffect, FUN.VALUE = 2)
lines(p038~PctAgree, data=RF, col=4, lty=5)

LegPos <- c(.05,.045)
if(RawVsReturn == 0) LegPos <- c(.07,.095)
  
legend(LegPos[1],LegPos[2], legend = c("0% Blank", "12.5% Blank", "37.5% Blank", "62.5% Blank"), lty = c(1,3,4,5), col = 1:4,cex=0.6 )
# 
# library(reshape)
# library(ggplot2)
# 
# mDF <- melt(RF,id.vars = "PctAgree")
# mDF
# 
# ggplot(mDF,aes(x = PctAgree, y = value, colour = variable, linetype = variable)) +
#   geom_line() +
#   ylim(-.06, .06)
# 



```

Audit
------------------
What is the effect of withholding "confusing" Decisions?

```{r HoldOff,cache=FALSE}

library(reshape)

DoubleFactoryTest <- function(X, Scales, Rep, CatchP=.1, MaxRow=5000, Phi=.65, Verbose=FALSE) {
  
    #Fill the default reputations (egalitarian) if none are provided...unrealistic and only for testing.
  if(missing(Rep)) { Rep <- ReWeight(rep(1,nrow(X)))
                     if(Verbose) print("Reputation not provided...assuming equal influence.")
  }
  
  #******************
  #Fill the default scales (binary) if none are provided. In practice, this would also never be used.
  if(missing(Scales)) { Scales <- matrix( c( rep(FALSE,ncol(X)),
                                             rep(0,ncol(X)),
                                             rep(1,ncol(X))), 3, byrow=TRUE, dimnames=list(c("Scaled","Min","Max"),colnames(X)) )
                        if(Verbose) print("Scales not provided...assuming binary (0,1).")
  }
  
  WaveOne <- Factory(X,Scales,Rep,CatchP,MaxRow,Verbose)
  
  print(" Wave One Complete.")
  
  
  # Find the contested contracts
  ContestParameter <- .65 # completely made up, for now
  
  Safe  <- ( WaveOne$Decisions["Certainty",] ) >= Phi # all those contracts which were unanimous for a subset of proportion ("Phi")
  
  print( sum(Safe)/ncol(X) ) # proportion which made it
  print( X[,Safe] )          # the new matrix
  
  WaveTwo <- Factory( X[,Safe] ,
                      Scales[,Safe],
                      Rep,CatchP,MaxRow,Verbose)
  
  Results <- matrix( c( WaveOne$Agents[,"RowBonus"], WaveTwo$Agents[,"RowBonus"] ),ncol=2,dimnames=list(rownames(X),c("One","Two")) )
  
  mRes <- melt(Results)
  cRes <- cast(mRes,formula=X1~X2,fun.aggregate=sum)
  
  print(cRes)
  
  Results <- cbind(Results, "Diff"=Results[,2]-Results[,1])
  
  return(Results)
  
}

DoubleFactoryTest(Scenarios$Base)

#          X1       One   Two
# 1 Distort 1 0.1717624 0.175
# 2 Distort 2 0.1717624 0.175
# 3      Liar 0.3000000 0.300
# 4      True 0.3564751 0.350

DoubleFactoryTest(Scenarios$CoalitionalDeviance)

#      X1        One        Two
# 1 Diver 0.08181818 0.08181818
# 2  Liar 0.35698136 0.36727273
# 3  True 0.56120046 0.55090909

# The attack has essentially been erased...


DoubleFactoryTest(Scenarios$CluelessTest)
# No difference

DoubleFactoryTest(Scenarios$Incoherence,CatchP=.2)

DoubleFactoryTest(Scenarios$Gaming,CatchP=.2)


Mz <- matrix( c(1, 1,.5, 0, 0, # real
                0, 1,.5, 0, 0, # attacker 1
                1, 0,.5, 0, 0), # attacker 2
              ncol=5,byrow=TRUE,dimnames=list(c("Honest","Attacker1","Attacker2"),c("C1.1","C2.1","C3.5","C4.0","C5.0")))
                
                
DoubleFactoryTest(Mz,Rep=c(.34,.30,.36))
DoubleFactoryTest(Mz,Rep=c(.34,.36,.30))

# Having more reputation actually HURTs the attack, by kicking it out of the second wave. Then, with the contested Decision out of the wave, a less-interested attacker bailing with Honest on one other Decision (one that they don't really care about). The majority attacker loses some of the influence he would have gained had he been able to flip more contracts.
# Knowing this, the minority attacker should be even more worried than usual.
# Facinating.

```

Double Factory Examination
===========================================

Here I go into even greater detail...in even more depth than the above.
```{r DefineDoubleFact}

Use('ggplot2')

## What effect does DoubleFactory have?

Dim <- 20

ContAmb <- matrix(0,(Dim-1),(Dim-1))
ContAmb[ lower.tri(ContAmb, diag = TRUE) ]  <- 1

# Balance the matrix
ContAmb <- cbind(ContAmb,0) 

# Add a few 'right answers'
ContAmb <- rbind(ContAmb[1:9,],
                 ContAmb[9,], ContAmb[9,],
                 ContAmb[10,], ContAmb[10,],
                 ContAmb[10:19,] ) 

colnames( ContAmb ) <- paste("D.",1:(ncol(ContAmb)), sep="") 
row.names( ContAmb ) <- paste("Voter.",1:(nrow(ContAmb)), sep="") 

ContAmb


DoubleFactoryTest <- function(X, Scales = BinaryScales(X), Rep = DemocracyRep(X), CatchP=.1, MaxRow=5000, Phi=.65, Verbose=FALSE, PrintSurvivors = TRUE) {
  # Runs Factory Twice and checks on what happened as a result
  
  WaveOne <- Factory(X,Scales,Rep,CatchP,MaxRow,Verbose)
  
  if(Verbose) print(" Wave One Complete.")
  
  
  # Find the contested contracts
  Safe  <- ( WaveOne$Decisions["Certainty",] >= Phi )# all those contracts which were unanimous for a subset of proportion ("Phi")
  
  # What if they ALL were contested?
  if( sum(Safe)==0 ) {
    print("Consensus Failure!! ..printing Wave one")
    print("Consensus Failure!! ..printing Wave one")
    print("Consensus Failure!! ..printing Wave one")
    return(WaveOne)
    }
  
  if(PrintSurvivors) {
    print( sum(Safe)/ncol(X) ) # proportion which made it
    print( X[,Safe] )          # the new matrix
  }
  
  WaveTwo <- Factory( X[,Safe] ,
                      Scales[,Safe],
                      Rep,CatchP,MaxRow,Verbose)
  
  Results <- matrix( c( ( WaveOne$Agents[,"RowBonus"] - WaveOne$Agents[,"OldRep"] ),
                        ( WaveTwo$Agents[,"RowBonus"] - WaveTwo$Agents[,"OldRep"] ) ),
                     ncol=2,
                     dimnames=list(rownames(X),c("Gain.W1","Gain.W2")) )
  
  mRes <- melt(Results)
  cRes <- dcast(mRes,formula=Var1~Var2,fun.aggregate=sum)
  
  Results <- cbind(Results, "Diff"=Results[,2]-Results[,1])
  
  PlotResults <- data.frame( cbind(Results, "Voter"=factor( 1:(nrow(Results)) )) )
  mPR <- melt(PlotResults,id.vars="Voter")
  
  P1 <- ggplot(mPR, aes(y=value, x=Voter, fill=factor( Voter ) )) +
    geom_bar(stat="identity", position = "dodge") +
    theme(legend.position="none") +
    facet_grid(variable~.)
  
  print(P1)
  
  return(Results)
  
}

```

```{r Tests}

DoubleFactoryTest(ContAmb)
# Comment: Here, because of this amusingly-unrealistic Voting Matrix (where nearly everyone is equally confused about everything),
# ...the 'Reference Index' is at zero. The software cannot establish a reference case, and is essentially indifferent.
# This is why Voters 1-8 benefit and 15-23. This is arbitrary and unstable, and might flip with just a fractional increase in 15-23 coordination.
# Double Factory seems to help in this case: the middle groups become more coordinated and less arbitrary.

ContAmb2 <- ContAmb
ContAmb2["Voter.23", "D.18"] <- 0 # The most profitable deviation (?)

DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)
# Voter 23 has sent his report skyrocketing...
DoubleFactoryTest(ContAmb, PrintSurvivors = FALSE)["Voter.23","Gain.W2"] # -0.004347826
DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)["Voter.23","Gain.W2"] # 0.003491191
# ...but the core group is mostly unaffected (improving slightly).
DoubleFactoryTest(ContAmb, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0003981117
DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0004388715


# The obvious counter-move:
ContAmb3 <- ContAmb2
ContAmb3["Voter.1", "D.3"] <- 1 # The most profitable deviation (?)

DoubleFactoryTest(ContAmb3)
# Voter 1 has reclaimed his position...
DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)["Voter.1","Gain.W2"] # -0.004347826  -- notice that this is actually the same as ContAmb1 Voter 23!
DoubleFactoryTest(ContAmb3, PrintSurvivors = FALSE)["Voter.1","Gain.W2"] # 0.003792857
# ...and the core group still marches slowly toward victory.
DoubleFactoryTest(ContAmb2, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0004388715
DoubleFactoryTest(ContAmb3, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0004328065

# Repeat repeat repeat...
ContAmb4 <- ContAmb3
ContAmb4["Voter.22", "D.17"] <- 0
ContAmb4["Voter.21", "D.16"] <- 0
ContAmb4["Voter.20", "D.15"] <- 0
# Voter 22 ...
DoubleFactoryTest(ContAmb3, PrintSurvivors = FALSE)["Voter.22","Gain.W2"] # -0.004347826
DoubleFactoryTest(ContAmb4, PrintSurvivors = FALSE)["Voter.22","Gain.W2"] # 0.003074838
# ...march, march, march.
DoubleFactoryTest(ContAmb3, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0004328065
DoubleFactoryTest(ContAmb4, PrintSurvivors = FALSE)["Voter.10","Gain.W2"] # 0.0006672369


```


```{r PhiEffect}

DoubleFactoryTest(ContAmb, Phi = .55)

DoubleFactoryTest(ContAmb, Phi = .70)

DoubleFactoryTest(ContAmb, Phi = .90)

DoubleFactoryTest(ContAmb, Phi = .95)

# The effect is clear: more stablity. W2 is simply "flatter" and less subject to the arbitrary tiebreaker of the Reference Index.

```


```{r BumpingInAndOut}

Bump <- ContAmb

Unbumped <- DoubleFactoryTest(Bump)

#Voter 8 Bumps Decision 8
Bump2 <- Bump
Bump2["Voter.8","D.8"] <- 0
Bumped <- DoubleFactoryTest(Bump2)

Unbumped["Voter.8","Gain.W2"]
Bumped["Voter.8","Gain.W2"]
# This is kind of strange...

# (1) There is a more profitable move availiable to Voter.8
# (2) This is a function of this strange matrix specifically

Bump3 <- Bump
Bump3["Voter.8","D.9"] <- 1

Unbumped["Voter.8","Gain.W2"]
DoubleFactoryTest(Bump3)["Voter.8","Gain.W2"]
# Ha, this is interesting...Voter 8 accidentally de-coordinated his misinformed group.

Bump <- matrix(0,(Dim-1),(Dim-1))
colnames( Bump ) <- paste("D.",1:(ncol(Bump)), sep="") 
row.names( Bump ) <- paste("Voter.",1:(nrow(Bump)), sep="") 
Bump[1:9,"D.1"] <- 1

DoubleFactoryTest(Bump)

# Clearly, if someone "un-Bumps" Decision 1, the "Bumpers" are screwed.

```




```{r Synthesis}

# Outcome of Phi / DoubleFactory
M_res <- M1[,2:3]

GetUniqueBallots( M_res )

GetAuditChoices( M_res )

GetContestedDecisions <- function(M) {
  # Puts a few pieces together
  
  Uncontested <- colnames( DoubleFactory(M)$Filled )
  ContestedMatrix <- M[,! (colnames(M) %in% Uncontested) ] # notice "!"
  return( GetAuditChoices( ContestedMatrix ) )
}

GetContestedDecisions(M1)
# $Choices
#   BallotGroup BallotRep D2.1 D3.0
# 1           A 0.3333333    1    0
# 4           D 0.3333333    0    1
# 
# $NonChoices
#   BallotGroup BallotRep D2.1 D3.0 SurrogateChoice
# 2           B 0.1666667    0    0             Tie
# 3           C 0.1666667    1    1             Tie

# Notice something interesting:
GetAuditChoices( M )
GetAuditChoices( M1[,2:3] )

# Notice also that I am NOT using SVD on purpose:
# [1] If we make it to this point, the attacker will have >50% ...
# [2] SVD had a specific purpose of measuring disagreement with the majority. However, this case is a failure-to-find-majority.

BigM1 <- cbind( M1, M1, M1, M1[,-3])

DoubleFactoryTest(BigM1)
GetContestedDecisions(BigM1)
PlotJ(BigM1)



#
colnames(VM6) <- paste("D",1:5,sep = ".")
Scales6 <- BinaryScales(VM6)
Scales6["Scaled",] <- TRUE
DoubleFactoryTest(VM6, Scales = Scales6, Rep = R6a)
GetAuditChoices(VM6,Reputation = R6a)
# This seems to be a successful attack ... but how strategically stable is it?

# ...if the 68% group waivers a little:
R6b <- c(.34, .32001, .33999)
GetAuditChoices(VM6,Reputation = R6b)
# $Choices
#   BallotGroup BallotRep D.1 D.2 D.3  D.4   D.5
# 1           A   0.34000 0.8   0   0 0.25 0.045
# 3           C   0.33999 0.4   1   1 0.15 0.015
# 
# $NonChoices
#   BallotGroup BallotRep D.1 D.2 D.3 D.4  D.5 SurrogateChoice
# 2           B   0.32001 0.6 0.5 0.5 0.2 0.03               C

# this results favors increasing the unique Ballots to 3, (perhaps, IF the current Ballots do not contain enough residual vote-distance)

# let's go back and add that.


# (later) ...added.

```


